### 2019-05-14 doc/leader/frontpage_with_picture.tex
titlepage

\fontsize{10pt}{12pt}\selectfont
\textbf{Description of thesis (semester- / Bachelor thesis / etc.)} \\		% Insert text
\vspace{3mm}

@@

\begin{textblock}{150}(28,225)
\fontsize{10pt}{17pt}\selectfont
\begin{tabbing}
xxxxxxxxxxxxxxx\=xxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxx \kill
Degree course:	\> [z.B. Electrical and Communication Engineering]	\\		% insert name of degree course
Authors:		\> [Test Peter, M\"uster R\"os\"a]		\\					% insert names
Tutor:	\> [Dr.~Xxxx Xxxx, Dr.~Yyyy Yyyy]		\\							% insert names
Constituent:	\> [Wwwww AG]					\\							% insert names
Experts:		\> [Dr.~Zzzz Zzzz]				\\							% insert names
Date:			\> \versiondate					\\							% read from file leader/version.tex
\end{tabbing}

>>>>

\fontsize{10pt}{12pt}\selectfont
\textbf{Bachelor thesis} \\		% Insert text
\vspace{3mm}

@@

\begin{textblock}{150}(28,225)
\fontsize{10pt}{17pt}\selectfont
\begin{tabbing}
xxxxxxxxxxxxxxx\=xxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxx \kill
Degree course:	\> Computer Science	\\		% insert name of degree course
Authors:		\> Anna Doukmak, Ramon Boss		\\					% insert names
Tutor:	\> Kai Brünnler @TODO Dr.?		\\							% insert names
%Constituent:	\> [Wwwww AG]					\\							% insert names
Experts:		\> Urs Keller				\\							% insert names
Date:			\> \versiondate					\\							% read from file leader/version.tex
\end{tabbing}
